ms_8

### 2020-04-25 ms_8.Rmd
plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
library(scales)
```

@@

@@

obesity_region_plot <- obesity_region %>% 
    filter(!is.na(region)) %>%
    ggplot(aes(color = region, x = year, y = mean_perc)) +
    geom_jitter(aes(alpha = 0.1), show.legend = FALSE) +
    theme_minimal() +
    labs(title = "Percent of Population Classified as Obese or Overweight \n in US Over Time by Region",
         caption = "Data from Center for Disease Control",
         x = "Mean Percent of Population",
         y = "Year",
         color = "Region") +
    geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
    facet_wrap(~ region)

@@

@@

food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
                                     color = "green", labels = FALSE) +
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "green", name = "Mean Poverty Rate") +
    labs(title = "Poverty Rate in the US",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau") +
    theme_void()
food_poverty_mean_plot

@@

@@

# compare % of people that're obese to % of people that're lia and la

@@

food_sum <- food_access %>% 
    group_by(state, urban, lia_pop, la_pop, region) %>% 
    summarise(total_pop = sum(popul),
           total_lia_pop = sum(lia_pop),
           total_la_pop = sum(la_pop),
           perc_lia = round((total_lia_pop/total_pop)*100, digits = 0),
           perc_la = round((total_la_pop/total_pop)*100, digits = 0),
           mean_poverty = round(mean(poverty), digits = 0)) %>% 
    select(-total_pop, -total_lia_pop, -total_la_pop, -la_pop, -lia_pop)

joined <- left_join(obesity_2011, food_sum, by = "state")

@@

Shiny App

 fluidPage(

    titlePanel("GOV1005 Final Project"),

    navlistPanel("Header A",
                 tabPanel("Component 1"),
                 "Header B",
                 tabPanel("Component 3"),
                 tabPanel("Component 4")
    ),

    sidebarLayout(position = "right",
        sidebarPanel(img(src = "cartoon.png", height = 140, width = 200)),
        mainPanel(h3("Red Meat Production in the US Over Time"),
                  imageOutput("meat_clean_plot"),
                  br(),
                  br(),
                  br(),
                  br(),
                  br(),
                  br(),
                  actionButton("action", "Click")
    )
)

)

# Define server logic required to draw a histogram
server <- function(input, output) {

    output$meat_clean_plot <- renderImage({
        list(src = "meat_clean_plot.png",
             contentType = 'image/png',
             width = 550,
             height = 500)},
        deleteFile = FALSE
    )  
}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
library(scales)
library(infer)
library(broom)
library(tidyverse)
library(ggcorrplot)
library(gt)
```

@@

saveRDS(obesity_mean, file = "obesity_mean.RDS")

@@

saveRDS(obesity_region, file = "./obesity_shiny/data/obesity_region.RDS")

obesity_region_plot <- obesity_region %>% 
    filter(!is.na(region)) %>%
    ggplot(aes(color = region, x = year, y = mean_perc)) +
    geom_jitter(aes(alpha = 0.1), show.legend = FALSE) +
    theme(panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank()) + 
    theme_minimal() +
    labs(title = "Percent of Population Classified as Obese or Overweight \n in US Over Time by Region",
         caption = "Data from Center for Disease Control",
         y = "Mean Percent of Population",
         x = "Year",
         color = "Region") +
    geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
    facet_wrap(~ region)

@@

saveRDS(food_access, file = "./obesity_shiny/data/food_access.RDS")

@@

saveRDS(food_poverty_mean, file = "./obesity_shiny/data/food_poverty_mean.RDS")

food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
                                     color = "white", labels = FALSE) +
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "blue", name = "Mean Poverty Rate") +
    labs(title = "Poverty Rate in the US",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau") +
    theme_void()
food_poverty_mean_plot

@@

saveRDS(food_lia, file = "./obesity_shiny/data/food_lia.RDS")

@@

@@

joined <- left_join(obesity_2011, food_sum, by = "state") %>% 
    mutate(region = case_when(
        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
                     "LA", "OK", "TX") ~ "South",
        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West"),
        urban = case_when(
            urban == 0 ~ "urban",
            urban == 1 ~ "rural")
    )

@@

```{r relationship between obesity and different variables}

sapply(joined, class)

joined <- joined %>% 
    ungroup() %>% 
    mutate(age = as.factor(age),
           gender = as.factor(gender),
           race = as.factor(race),
           urban = as.factor(urban),
           region = as.factor(region))

joined_cor <- joined %>% 
    mutate("Obesity Rate" = mean_perc_obese,
           "% Low Income and Food Access" = perc_lia,
           "% Low Food Access" = perc_la,
           "Poverty Rate" = mean_poverty) %>% 
    select("Obesity Rate", "% Low Income and Food Access", "% Low Food Access", "Poverty Rate") %>% 
    cor()

corrplot <- ggcorrplot(joined_cor, 
             type = "upper", 
             colors = c("blue", "white", "blue"),
             lab = TRUE,
             lab_size = 4,
             lab_col = "black",
             ggtheme = theme_void) +
             labs(title = "Correlations Between Obesity, \n Poverty, and Food Access")  + 
             theme(plot.title = element_text(hjust = 0.5, size = 15),
                   legend.position = "none")

ggsave("plots/corr_plot.png", plot = corrplot)

```{r gt}

#yield a graph showing how the mean percentage of obesity is affected by different variables

bootstrap_joined <- joined %>% 
  rep_sample_n(size = 50, replace = TRUE, reps = 1000) %>% 
  group_by(replicate)

saveRDS(bootstrap_joined, file = "./obesity_shiny/data/bootstrap_joined.RDS")

joined_lm_lia <- lm(mean_perc_obese ~ perc_lia, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_lia_gt <- joined_lm_lia %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Low Food Access and Low Income on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

gtsave(joined_lm_lia_gt, "lia_gt.html")

joined_lm_gender <- lm(mean_perc_obese ~ gender, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_gender_gt <- joined_lm_gender %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Gender on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

gtsave(joined_lm_gender_gt, "gender_gt.html")

joined_lm_age <- lm(mean_perc_obese ~ age, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
    select(term, estimate, conf.low, conf.high) %>% 
    mutate(
      estimate = round(estimate, digits = 3),
      conf.low = round(conf.low, digits = 3),
      conf.high = round(conf.high, digits = 4))

joined_lm_age_gt <- joined_lm_age %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Age on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

joined_lm_race <- lm(mean_perc_obese ~ race, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_race_gt <- joined_lm_race %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Race on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

joined_lm_la <- lm(mean_perc_obese ~ perc_la, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_la_gt <- joined_lm_la %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Low Food Access on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

joined_lm_urban <- lm(mean_perc_obese ~ urban, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_urban_gt <- joined_lm_urban %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Ruralness on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

joined_lm_mean_poverty <- lm(mean_perc_obese ~ mean_poverty, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_poverty_gt <- joined_lm_mean_poverty %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Poverty on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

joined_lm_region <- lm(mean_perc_obese ~ region, data = bootstrap_joined) %>% 
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>% 
  mutate(
    estimate = round(estimate, digits = 3),
    conf.low = round(conf.low, digits = 3),
    conf.high = round(conf.high, digits = 4))

joined_lm_region_gt <- joined_lm_region %>% 
  gt() %>% 
  tab_header(
    title = "Effect of Region in the US on Average Percentage of Obesity in a Population") %>%
  cols_label(
    term = "Variable", 
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Higher Bound") %>% 
   tab_spanner(
    label = "Data from 2010 Census Bureau, USDA, and CDC",
    columns = vars(term, estimate, conf.low, conf.high))

joined_poverty_obesity <- bootstrap_joined %>% 
  ggplot(aes(x = mean_poverty, y = mean_perc_obese)) +
  geom_jitter(aes(color = urban)) +
  scale_color_manual(values = c("purple", "dark red")) +
  theme_minimal() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank()) +
  labs(title = "Poverty Rate on Obesity Rate",
       caption = "Data from US Department of Agriculture and 2010 Census Bureau",
       color = "Ruralness",
       x = "Mean Poverty Rate",
       y = "Mean Obesity Rate") +
  geom_smooth(method = "lm", color = "black")
joined_poverty_obesity

An Introduction

- Introduce the issue
- Describe what obesity is 
- Describe what food insecurity is

Variables in question

Obesity
Obesity over time map
Choose region to look at map
The poverty map
Should make a graph showing how poverty relates to obesity

Food lia
Could allow people to choose between which regions they want to compare

Findings
Correlation plot
Make best fit line graphs for each variable that affects obesity and allow people to choose which one they want to look at
Make a regression plot
  Otherwise, gt tables?

Data
Give process of creation of the data 
Give sources

Me
Self introdcution
Provide links to github and linkedin
